---
title: "Data Completeness Report (v1.1)"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: spacelab
    source_code: embed
runtime: shiny
resource_files:
- data/Fields_DataCompleteness_270302_20210110.xlsx
---

```{r setup, include=FALSE}
library(tidyverse)
library(janitor)
library(reactable)
library(flexdashboard)
library(readxl)
library(htmltools)
library(noteMD)
library(knitr)
# helpers 
# source("helpers.R")
```

```{r helpers, include=FALSE, eval=TRUE}
# miss_filter function -----------------------------------------------
miss_filter <- function(data) { 
  
  MissDataFields <- filter(.data = data, `# Missing` > 0)
  
  return(MissDataFields)
  
}

# critical_miss_filter function -----------------------------------------------
critical_miss_filter <- function(data) { 
  
  CritDataFields <- filter(.data = data, `Dataset Name` %in% 
                             c("ECIF", "MHB", "CEB", "QSEM", "AE"))
  
  CritMissDataFields <- filter(.data = CritDataFields, `# Missing` > 0)
  
  
  return(CritMissDataFields)
  
}


# critical_filter function ------------------------------------------------
# this function will filter the data based on the check-box input

critical_filter <- function(data) { 
  
  CritDataFields <- filter(.data = data, `Dataset Name` %in% 
                             c("ECIF", "MHB", "CEB", "QSEM", "AE"))
  
  return(CritDataFields)
  
}
```

```{r reactives}
# identify data path
app_data_path <- fs::dir_ls(path = "data", regexp = "\\.xlsx$")
# load the Fields Listing sheet
FieldsInput <- reactive({
  read_excel(app_data_path, 
    sheet = "Fields Listing")
})

# load the Removed Listing sheet
RemovedInput <- reactive({
    read_excel(app_data_path, 
      sheet = "Removed Listing")
})
```

```{r FieldsFinalInput-reactive, eval=TRUE}
FieldsFinalInput <- reactive({
    # the Fields Listing sheet enters the app with rows, but the 
    # checkboxGroupInput allows the user to filter the data to either: 
    # 
    # 1) only critical and missing fields  
    if (all(c("critical", "missing") %in% input$critical_miss)) {
      
      critical_miss_filter(FieldsInput())
      
    # 2) only critical fields
    } else if (all(c("critical") %in% input$critical_miss)) {
      
      critical_filter(FieldsInput())
    
    # 3) only missing fields
    } else if ("missing" %in% input$critical_miss) {
      
      miss_filter(FieldsInput())
    
    # if nothing is selected, we see the entire listing.
    } else {
      
      return(FieldsInput())
      
    }
    
})
```

```{r FieldsFinalInput-eventReactive, eval=FALSE}
# NOT RUN ----
# this is another option for filtering to critical and missing, but it uses a
# 'submit' button (then creates the selected input)
FieldsFinalInput <- eventReactive(input$submit_critical_miss, {

    # 1) only critical and missing fields
    if (all(c("critical", "missing") %in% input$critical_miss)) {

      critical_miss_filter(FieldsInput())

    # 2) only critical fields
    } else if (all(c("critical") %in% input$critical_miss)) {

      critical_filter(FieldsInput())

    # 3) only missing fields
    } else if ("missing" %in% input$critical_miss) {

      miss_filter(FieldsInput())

    # if nothing is selected, we see the entire listing.
    } else {

      FieldsInput()

    }

})
```

Sidebar {.sidebar data-width=320}
=====================================

### Dashboard use

Both the **Fields Listing** and **Removed Listing** sheets are presented in sortable and filterable tables. 

***

#### Filter Fields Listing

Use the checkboxes below to filter the **Fields Listing** to only critical variables or variables with missing values.

```{r checkboxInput-critical}
checkboxGroupInput(inputId = "critical_miss", label = "Filter listing", 
                   choices = c("critical", "missing"))
```

```{r checkboxInput-only_miss, eval=FALSE}
# NOT RUN ----
# see FieldsFinalInput-eventReactive above
actionButton(inputId = "submit_critical_miss",
            label = "Submit")
```

***

#### Download Report

Select the document format and click the **Download** button. 

```{r downloadButton-describe_download}
downloadButton(
  outputId = "describe_download", # <- describe_download outputId ----
  label = "Download Report",
  class = "butt"
)
```

```{r radioButtons-format}
radioButtons(
  inputId = "format", # <- format outputId ----
  label = "Document format",
  choices = c("PDF", "Word"),
  inline = TRUE
  
)
```

```{r downloadHandler}
downloadHandler(
  # **create file name** ----
  filename = function() {
    paste("Summary", Sys.Date(), 
          switch(EXPR = input$format, 
                 PDF = ".pdf", 
                 Word = ".docx"), 
          sep = "")
  },
  # **(PDF) create content** ----
  content = function(file) {
    if (input$format == "PDF") {

      # **(PDF) start of progressing indicator** ----
      withProgress(
        message = "Download in progress",
        detail = "This may take a while...",
        value = 0,
        {
          for (i in 1:15) {
            incProgress(1 / 15)
            Sys.sleep(0.01)
          }
          # **(PDF) end of progression** ----

          src <- normalizePath("summary_report.Rmd")
          # temporarily switch to the temp dir, in case you do not have write
          # permission to the current working directory
          owd <- setwd(tempdir())
          on.exit(setwd(owd))

          file.copy(src, "summary_report.Rmd", overwrite = TRUE)

          library(rmarkdown)
          out <- render("summary_report.Rmd", pdf_document())
          file.rename(out, file)
        }
      )
      # **end of pdf content** ----
    } else {
      # **(DOCX) create content** ----
      # **(DOCX) start of progressing indicator** ----
      withProgress(
        message = "Download in progress",
        detail = "This may take a while...",
        value = 0,
        {
          for (i in 1:15) {
            # incremental progress
            incProgress(1 / 15)
            # set the Sys.sleep time
            Sys.sleep(0.01)
          }
          # (DOCX) end of progression ----

          src <- normalizePath("summary_report_word.Rmd")
          # temporarily switch to the temp dir, in case you do not have write
          # permission to the current working directory
          owd <- setwd(tempdir())
          on.exit(setwd(owd))
          file.copy(src, "summary_report_word.Rmd", overwrite = TRUE)

          library(rmarkdown)
          out <- render("summary_report_word.Rmd", word_document())
          file.rename(out, file)
        }
      )
    }
  }
)
```

***

#### Use

Use the empty boxes in each column to identify dataset, variables, or values. 

Click on the column names to sort the data. 

Beneath each table is a text-box for taking notes. These will be included in your downloaded report. Read more about markdown syntax [here.](https://www.markdowntutorial.com/)

***

#### Run Date Info

**Title:** Data Completeness - Listing of Fields    
**Study ID:** 270-302    
**Created on:** 2021-01-10 17:32  
**Data last updated on:** 2021-01-09


Fields Listing
=======================================================================

Row 
-----------------------------------------------------------------------

### Fields Listing table {data-height=800}


```{r FieldsListing-data}
renderReactable({
  
reactable(FieldsFinalInput(), 
          resizable = TRUE, 
          showPageSizeOptions = TRUE, 
          onClick = "expand", 
          highlight = TRUE, 
          filterable = TRUE, 
          minRows = 10)
})
```



Row 
-----------------------------------------------------------------------

### Fields Listing Notes {data-height=200}

```{r helpText-textarea-markdowninput_table_1}
# helpText for note 1 ----
helpText("Enter markdown text below:")
# textarea id for note 1 ----
# create id with the 'markdowninput_' prefix!
tags$textarea(
  "Please use **markdown** syntax!",
  id    = "markdowninput_table_1",
  rows  = 3,
  style = "width:100%;"
)
```

```{r reactive-htmloutput_table_1}
# reactive htmloutput_table_1 notes table 1 ---- 
# defines a reactive using the 'id' value from 'textarea'
# (id with `markdowninput` prefix) to create an 'output' with the
# noteMD::note_in_html() function. The output object should use the 
# 'htmloutput_' prefix!
output$htmloutput_table_1 <- reactive({
  noteMD::note_in_html(input$markdowninput_table_1)
})
```

```{r helpText-and-define-htmlOutput-outputId-as-htmloutput_table_1}
# helpText for Preview note 1 ----
# This is the text that falls directly below the text box for the notes
helpText("Preview formatted text:")
# htmlOutput ----
# Now we can render the HTML with htmlOutput() using the reactive we created 
# with the noteMD::note_in_html() (with the htmloutput_ prefix)
htmlOutput(outputId = "htmloutput_table_1")
```


Removed Listing 
=======================================================================

Row 
-----------------------------------------------------------------------

### Removed Listing Table {data-height=800}

```{r RemovedListing-data}
renderReactable({
reactable(RemovedInput(), 
          resizable = TRUE, 
          showPageSizeOptions = TRUE, 
          onClick = "expand", 
          highlight = TRUE, 
          filterable = TRUE, 
          minRows = 10)
})
```

Row 
-----------------------------------------------------------------------

### Removed Listing Notes {data-height=200}

```{r helpText-and-define-textarea-id-as-markdowninput_table_2}
# helpTex notes table 2 ----
# this is displayed above the text box 
helpText("Enter markdown text below:")
# textarea id (use markdowninput prefix!) 
tags$textarea(
  "Please use **markdown** syntax!",
  id    = "markdowninput_table_2",
  rows  = 3,
  style = "width:100%;"
)
```

```{r note_in_html-markdowninput_table_2-htmloutput_table_2}
# reactive({}) note_in_html notes table 2 ---- 
# defines this as a reactive using the `input` value from `textarea` 
# (with `markdown_` prefix), which is placed inside noteMD::note_in_html().
#  The `outputId` comes from the htmlOutput() (with the 
# `htmloutput_` prefix). 
output$htmloutput_table_2 <- reactive({
  noteMD::note_in_html(input$markdowninput_table_2)
})
```

```{r helpText-and-define-htmlOutput-outputId-as-htmloutput_table_2}
# helpText preview notes table 2 ----
# This is the text that falls directly below the text box for the notes
helpText("Preview formatted text:")
# htmlOutput = use htmlmarkdown prefix!
htmlOutput(outputId = "htmloutput_table_2")
```


